\chapter{Introduction}
This document explains the strategies used for Left 4 Dead and Left 4 Dead 2 survival mode. I wrote a lot of these strategies down for the group ``North American Survivors'' and because I enjoyed doing so, I wanted to record them in a more permanent spot. This document is a work-in-progress. It's time consuming to write down all the details of the strategies used and there are also multiple strategies in many of the maps. Some of the maps do not have many details in this document, but this will hopefully be changed in the future.

\section{Purpose}
When first starting off with the game, it might seem that survival mode has very little depth, does not last very long, and is tedious and repititious. On the contrary, survival mode offers intense, challenging, and fun games with a lot of replayability, however, there is a lot of teamwork and strategy required. New players have not been exposed to the teamwork and strategy when they first start off, and perhaps even encounter people trying to exploit or ``glitch'' their way to gold medals on survival mode. This document will serve as a guide to new players and veteran players alike who want to see a thorough explanation of the survival strategies that they can use in their games with the right team of players.

There are many people playing survival mode in Left 4 Dead and Left 4 Dead 2 from all over the world, and it is a good opportunity to make new online friends and collaborate with them towards a common goal. The Left 4 Dead series are known to be high quality cooperative games that stress teamwork, and the addition of goals and records makes the game refreshing and endlessly replayable for many survival enthusiasts.

\paragraph{Other Game Modes?}
This guide applies to survival mode only. A lot of the strategies rely on how the A.I. work on the map and where the A.I. spawn and although some of the strategies may carry over to versus, versus survival, or scavenge, a lot of them will be ineffective. This strategies will easily apply to campaign mode, however, campaign mode is much easier due to the fact that the tanks do not spawn with horde of common infected. Campaign mode simply does not require such detailed strategies.

\section{Left 4 Dead or Left 4 Dead 2?}
Each of the two games have a very distinct flavor in survival mode. Left 4 Dead is a short-range map where the focus is on positioning to block chokepoints and to use the ammo conservatively. Left 4 Dead 2 is more long-range and there is more mobility involved. Overall, Left 4 Dead 2 is the more difficult game, however, some maps in Left 4 Dead 2 are easier than maps in Left 4 Dead. Some players prefer one game over the other, but I personally enjoy both games. New players can begin in either game.

\section{Format of this Guide}
The guide contains one section for each of the maps in both Left 4 Dead and Left 4 Dead 2. First, the positions that each of the four players should use are listed. Then, a number of helpful comments about the strategy are provided as notes.

\section{Acknowledgements}
Thanks goes to \texttt{TheKevSham}, \texttt{Licksore}, and \texttt{sauce} who wrote some of these strategies.
